Draft: Judicial independence and post-election protest

### 2022-02-21 Output/manipulation_protest_draft.Rmd
Updates to intro

>>>>

Just as many less democratic states have enshrined multiparty elections into their political systems in the post-Cold War period, many have simultaneously experimented with varying degrees of judicial independence. A growing research tradition identifies various benefits that more independent courts can provide for non-democratic ruling parties, including regime legitimation, monitoring of discontent and of abuses by low-level officials, protecting investments, and more [@Moustafa2008]. As a result of these benefits, even many of the most authoritarian states have added de jure protections for courts's autonomy to their laws and constitutions [Staton2020]. At the same time, just like elections, more independent courts create an unpredictable connection between state and society; more open courts create opportunities for legal mobilization against the regime, with uncertain consequences. Consequently, de-democratizing states may act to restrain previously independent courts.

These dynamics can be seen across Europe, from legal contestation in Ukraine and Russia [@popova2020politicized] to the erosion of judicial independence in Poland and Hungary. In the latter case, the ruling Law and Justice Party (PiS) has taken significant steps to weaken judicial independence since 2015. These include increasing the legislature's influence over judicial appointments, stacking the judicial-nomination council with ruling-party allies, and the creation of a disciplinary chamber under the control of the Ministry of Justice. This disciplinary body can impose salary cuts, or even dismissal, on judges found to have in vaguely-defined "political activity"---which includes discussions of judicial independence and the PiS reforms themselves [@Duncan2020]. The situation has raised sufficient alarm among other EU member states that the European Commission has announced an infringement procedure against Poland, for flouting EU law while undermining its national courts' autonomy (https://www.dw.com/en/eu-starts-new-legal-action-against-poland-over-rule-of-law/a-60220102). Similarly, in Hungary, the parliamentary majority created a new National Office for the Judiciary in 2012, with broad powers to appoint and promote judges (https://www.venice.coe.int/Newsletter/NEWSLETTER_2012_02/1_HUN_EN.html).
